---
title: "HW3"
output: word_document
---

##Create snapshots with node size=3 and the following network layouts. 

```{r setup, include=FALSE}
library(igraph)
link <- read.csv("/Users/QiJin/Downloads/Dataset3-Airlines-EDGES.csv",header = T,as.is = T)
node <- read.csv("/Users/QiJin/Downloads/Dataset3-Airlines-NODES.csv",header = T,as.is = T)
nets <- graph.data.frame(link, node, directed=T) 
nets <- simplify(nets, remove.multiple = F, remove.loops = T)
```

## 1.1
Create a snapshot of the network with node color as red, node size as 10 and no node labels. See the example below.

```{r 1.1}
plot(nets, edge.arrow.size=0, edge.color="black",
     vertex.color="red",vertex.frame.color="black", vertex.color="red",
     vertex.label="")
```

## 1.2

Create a snapshot where the node shape is square.

```{r 1.2}
V(nets)$shape = "square"

plot(nets,edge.arrow.size=0, edge.color="black",
     vertex.color="red",vertex.frame.color="black", vertex.color="red",
     vertex.label=NA)
```

## 1.3
Calculate the degree of nodes and change the node size using the formula (node size=degree*0.2).

```{r 1.3}
V(nets)$shape = "circle"
deg <- degree(nets, mode="all")
V(nets)$size <- deg*.2
plot(nets, edge.arrow.size=0, edge.color="black",
     vertex.color="red",vertex.frame.color="black", vertex.color="red",
     vertex.label="")
```

##1.4 
Create snapshot of the network where the node size = 10.

```{r 1.4}
V(nets)$size <- 10
plot(nets, edge.arrow.size=0, edge.color="black",
     vertex.color="red",cex =10, vertex.frame.color="black", vertex.color="red",
     vertex.label="")
```

##1.5 
Color nodes according to visits.Look for visit column in the node data frame.
Assign a color to all the nodes below 100 visits and assign a different color to all the nodes number of visits equal to more than 100.

```{r 1.5}
col <- unique(V(nets)$Visits)

pal <- rainbow(400, alpha=.5)

V(nets)$color <- pal[V(nets)$Visits]

plot(nets, edge.arrow.size=0, edge.color="black",cex =10, vertex.frame.color="black",
     vertex.label=NA)
#?????????????????????????
```

##1.6 
Create a snapshot of the network where the node size=3 and the edge width is set according to link$Freq.

```{r 1.6}
E(nets)$width <- E(nets)$Freq/30
V(nets)$size <- 3
plot(nets, edge.arrow.size=0, edge.color="black",cex =10, vertex.frame.color="black",
     vertex.label=NA)
```

##Problem 2 
Create snapshots with node size=3 and the following network layouts.

```{r setup2,include=FALSE}
link <- read.csv("/Users/QiJin/Downloads/Dataset3-Airlines-EDGES.csv",header = T,as.is = T)
node <- read.csv("/Users/QiJin/Downloads/Dataset3-Airlines-NODES.csv",header = T,as.is = T)
nets <- graph.data.frame(link, node, directed=T) 
nets <- simplify(nets, remove.multiple = F, remove.loops = T)
V(nets)$size <- 3
E(nets)$width <- 0.2
```

##2.1 Randomlayout

```{r 2.1}
plot(nets, edge.arrow.size=0, edge.color="black",
     vertex.color="red",vertex.frame.color="black", vertex.color="red",
     vertex.label="",layout=layout.random)
```

##2.2 Circularlayout

```{r 2.2}
plot(nets, edge.arrow.size=0, edge.color="black",
     vertex.color="red",vertex.frame.color="black", vertex.color="red",
     vertex.label="",layout=layout.circle)
```

##2.3 3DSpherelayout

```{r 2.3}
plot(nets, edge.arrow.size=0, edge.color="black",
     vertex.color="red",vertex.frame.color="black", vertex.color="red",
     vertex.label="",layout=layout.sphere)
```

##2.4 FruchtermanReingoldlayout

```{r 2.4}
plot(nets, edge.arrow.size=0, edge.color="black",
     vertex.color="red",vertex.frame.color="black", vertex.color="red",
     vertex.label="",layout=layout.fruchterman.reingold)
```

##2.5 KamadaKawailayout

```{r 2.5}
plot(nets, edge.arrow.size=0, edge.color="black",
     vertex.color="red",vertex.frame.color="black", vertex.color="red",
     vertex.label="",layout=layout.kamada.kawai)
```

##2.6 Springlayout

```{r 2.6}
l <- layout.spring(nets, mass=.5)
plot(nets, edge.arrow.size=0, edge.color="black",
     vertex.color="red",vertex.frame.color="black", vertex.color="red",
     vertex.label="",layout=l)
```

##2.7 Lgllayout

```{r 2.7}
plot(nets, edge.arrow.size=0, edge.color="black",
     vertex.color="red",vertex.frame.color="black", vertex.color="red",
     vertex.label="",layout=layout.lgl)
```

##2.8 GEMlayout

```{r 2.8}
plot(nets, edge.arrow.size=0, edge.color="black",
     vertex.color="red",vertex.frame.color="black", vertex.color="red",
     vertex.label="",layout=layout.gem)
```